Lentiptical galaxies and their ordinary black holes

### 2015-07-08 papers/lentiptical/lentiptical.tex
welcomeback

\documentclass[preprint2]{aastex}

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
%%\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/results/plots/}}

@@

\shorttitle{Mbh-n paper}
\shortauthors{Savorgnan et al.}

@@

\title{Mbh-n paper}

@@

\begin{abstract}
blah blah
\end{abstract}

@@

%% From the front matter, we move on to the body of the paper.
%% In the first two sections, notice the use of the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below. We have
%% chosen the first three characters of the first author's name plus
%% the last two numeral of the year of publication as our KEY for
%% each reference.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so by tagging
%% their objects with \objectname{} or \object{}.  Each macro takes the
%% object name as its required argument. The optional, square-bracket 
%% argument should be used in cases where the data center identification
%% differs from what is to be printed in the paper.  The text appearing 
%% in curly braces is what will appear in print in the published paper. 
%% If the object name is recognized by the data centers, it will be linked
%% in the electronic edition to the object data available at the data centers  
%%
%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
%% the brackets must be escaped with backslashes when used in the first
%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
%%  Otherwise, LaTeX will issue an error.

@@

%%A focal problem today in the dynamics of globular clusters is core collapse.
%%It has been predicted by theory for decades \citep{hen61,lyn68,spi85}, but
%%observation has been less alert to the phenomenon. For many years the
%%central brightness peak in M15 \citep{kin75,new78} seemed a unique anomaly.
%%Then \citet{aur82} suggested a central peak in \object{NGC 6397}, and a
%%limited photographic survey of ours \citep[Paper I]{djo84} found three more
%%cases, \objectname{NGC 6624}, \objectname[M 15]{NGC 7078}, and
%%\object[Cl 1938-341]{Terzan 8}), whose sharp center had often been
%%remarked on \citep{can78}.
%%
%%As an example of how the new AASTeX object tagging macros work, we will
%%cite some of the ``Superlative'' objects mentioned in section 10 of
%%Trimble's (1992) review of astrophysics in the year 1991.  The youngest
%%star yet found was \object[\[JCC87\] IRAS 4]{IRAS 4} in \objectname{NGC 1333}.
%%\object{70 Oph} was found to be the longest period spectroscopic binary.
%%The most massive white dwarf was \object{GD 50}, estimated at 1.2 solar masses.
%%The first neutral hydrogen found in a globular cluster was \object{NGC 2808}
%%while the \objectname[SDSS J093401.92+551427.9]{I Zw 18} retained the
%%record for metal deficiency.  However, another low metallicitity
%%galaxy was \object{UGC 4483} in the \objectname{M 83} group. The
%%largest redshift \object[PC 1247+3406]{source} in 1991 was found at
%%z=4.897.  Lastly, what paper would be complete without a mention of the
%%\object[M1]{Crab nebula}!

\section{Errors}

How do we compute the errors on the measured S\'ersic indices?
Montecarlo, bootstrapping or any other evil statistical method do not take into account the systematics,
which mainly depend on the decomposition model, i.e. the choice of the model components.
But we are lucky, since there are many other decompositions in the literature for our galaxies.
\cite{grahamdriver2007,laurikainen2010,sani2011,vika2012,beifiori2012,rusli2013,lasker2014data} have done this job.
So how about we do something similar to our first paper?
Let's say that I am not better than anybody else at decomposing galaxies 
(this is obviously absurd, given my incredible competence in vivisecting galaxies, but let's assume it for now).
I repeat the same game we did in our first paper.
For each galaxy, I take all the available measurements from the literature, including my own measurement,
and I compute the standard deviation of each set of measurements.
The standard deviation becomes the error of my own measurement.
When my measurement is the only available (nobody other than me ever decomposed that galaxy),
the errors is set to be equal to the median value of the distribution in Figure \ref{fig:hist} 
(almost the same we did in our first paper, see footnote 4).
Figure \ref{fig:hist}: here only galaxies with more than one measurement are contributing.
Take a galaxy, take its set of measurements (more than one!) of the S\'ersic index, 
compute the standard deviation of that set, the standard deviation becomes the error on my own measurement
(BTW, I am using the $n$ derived from the equivalent axis fit).
The distribution of the standard deviations is represented by the histogram.
The median value is $0.13$, which means a median uncertainty of $33\%$ on each individual measurement.
If we take of each set of measurements the average, then the error associated to the average 
and then the median value of all these errors, basically we are doing the same we did in footnote 4 of our first paper,
and the cool thing is that now we get the same number we got then ($20\%$).

\begin{figure}
\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/auxiliary/histo_err_logn.eps}
\caption{}
\label{fig:hist}
\end{figure}

\section{Results}

Figure \ref{fig:mbhn}: Well, we now have the errors on each of OUR measurements of $n$.
We can plot bh mass vs $n$ (in log).

\begin{figure}
\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_logn.eps}
\caption{}
\label{fig:mbhn}
\end{figure}

Figure \ref{fig:mbhavn}: Almost the same we did in our first paper. We take for each galaxy its set of measurements of $n$,
we reject measurements in disagreement for more than $50\%$,
we compute the median (not the average! this is different from what we did in the past, what do you think?) 
and the error associated to the mean, then we plot the black hole masses vs the median of log(n).
The correlation looks a bit steeper than in Figure \ref{fig:mbhn}, 
with less scatter. I bet you say it looks curved.

PS I will soon step back from the division bulges/ellipticals, 
I seriously believe there is no such division. 
I will explain this soon. ;)

\begin{figure}
\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_median_logn.eps}
\caption{}
\label{fig:mbhavn}
\end{figure}

@@

%% In a manner similar to \objectname authors can provide links to dataset
%% hosted at participating data centers via the \dataset{} command.  The
%% second curly bracket argument is printed in the text while the first
%% parentheses argument serves as the valid data set identifier.  Large
%% lists of data set are best provided in a table (see Table 3 for an example).
%% Valid data set identifiers should be obtained from the data center that
%% is currently hosting the data.
%%
%% Note that AASTeX interprets everything between the curly braces in the 
%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
%% compile your manuscript.  Special characters do not 
%% need to be escaped in the optional, square-bracket argument.

%% All our observations were short direct exposures with CCD's.  We also have
%% a random {\it Chandra} data set \dataset{ADS/Sa.ASCA\#X/86008020} and a
%% neat \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum} that readers can access
%% via the links in the electronic edition.  Unfortunately this has nothing
%% whatsoever to do with this research.  At Lick Observatory we used a TI 500$\times$500
%% chip and a GEC 575$\times$385, on the 1-m Nickel reflector.  The only
%% filter available at Lick was red.  At CTIO we used a GEC 575$\times$385, with
%% $B, V,$ and $R$ filters, and an RCA 512$\times$320, with $U, B, V, R,$ and $I$
%% filters, on the 1.5-m reflector. In the CTIO observations we tried to
%% concentrate on the shortest practicable wavelengths; but faintness, reddening,
%% and poor short-wavelength sensitivity often kept us from observing in $U$ or
%% even in $B$. All four cameras had scales of the order of 0.4 arcsec/pixel, and
%% our field sizes were around 3 arcmin.
%%
%% The CCD images are unfortunately not always suitable, for very poor
%% clusters or for clusters with large cores.  Since the latter are easily
%% studied by other means, we augmented our own CCD profiles by collecting
%% from the literature a number of star-count profiles
%% \citep{kin68,pet76,har84,ort85}, as well as photoelectric profiles
%% \citep{kin66,kin75} and electronographic profiles \citep{kro84}.
%% In a few cases we judged normality by eye estimates on one of the Sky
%% Surveys.

%% In this section, we use  the \subsection command to set off
%% a subsection.  \footnote is used to insert a footnote to the text.

%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% This section also includes several of the displayed math environments
%% mentioned in the Author Guide.

%%\section{Helicity Amplitudes}
%%
%%It has been realized that helicity amplitudes provide a convenient means
%%for Feynman diagram\footnote{Footnotes can be inserted like this.}
%%evaluations.  These amplitude-level techniques
%%are particularly convenient for calculations involving many Feynman
%%diagrams, where the usual trace techniques for the amplitude
%%squared becomes unwieldy.  Our calculations use the helicity techniques
%%developed by other authors \cite[]{hag86}; we briefly summarize below.
%%
%%\subsection{Formalism} \label{bozomath}
%%
%%%% The equation environment wil produce a numbered display equation.
%%
%%A tree-level amplitude in $e^+e^-$ collisions can be expressed in
%%terms of fermion strings of the form
%%\begin{equation}
%%\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
%%\hat a_nu(p_1,\sigma_1) ,
%%\end{equation}
%%where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
%%and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
%%and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
%%operator $(\tau = \pm1)$.  The $a^\mu_i$ may be formed from particle
%%four-momenta, gauge-boson polarization vectors or fermion strings with
%%an uncontracted Lorentz index associated with final-state fermions.
%%
%%%% The \notetoeditor{TEXT} command allows the author to communicate
%%%% information to the copy editor.  This information will appear as a
%%%% footnote on the printed copy for the manuscript style file.  Nothing will
%%%% appear on the printed copy if the preprint or
%%%% preprint2 style files are used.
%%
%%%% The eqnarray environment produces multi-line display math. The end of
%%%% each line is marked with a \\. Lines will be numbered unless the \\
%%%% is preceded by a \nonumber command.
%%%% Alignment points are marked by ampersands (&). There should be two
%%%% ampersands (&) per line.
%%
%%In the chiral \notetoeditor{Figures 1 and 2 should appear side-by-side in
%%print} representation the $\gamma$ matrices are expressed
%%in terms of $2\times 2$ Pauli matrices $\sigma$ and the unit matrix 1 as
%%\begin{eqnarray}
%%\gamma^\mu  & = &
%% \left(
%%\begin{array}{cc}
%%0 & \sigma^\mu_+ \\
%%\sigma^\mu_- & 0
%%\end{array}	  \right) ,
%% \gamma^5= \left(
%%\begin{array}{cc}
%%-1 &   0\\
%%0 &	1
%%\end{array}	  \right)  , \nonumber \\
%%\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , \nonumber
%%\end{eqnarray}
%%giving
%%\begin{equation}
%%\hat a= \left(
%%\begin{array}{cc}
%%0 & (\hat a)_+\\
%%(\hat a)_- & 0
%%\end{array}\right), (\hat a)_\pm=a_\mu\sigma^\mu_\pm ,
%%\end{equation}
%%The spinors are expressed in terms of two-component Weyl spinors as
%%\begin{equation}
%%u=\left(
%%\begin{array}{c}
%%(u)_-\\
%%(u)_+
%%\end{array}\right), v={\bf (}\vdag_+{\bf ,}	\vdag_-{\bf )} .
%%\end{equation}
%%
%%%% Putting eqnarrays or equations inside the mathletters environment groups
%%%% the enclosed equations by letter. For instance, the eqnarray below, instead
%%%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%%%% LaTeX the paper and look at the output to see the results.
%%
%%The Weyl spinors are given in terms of helicity eigenstates
%%$\chi_\lambda(p)$ with $\lambda=\pm1$ by
%%\begin{mathletters}
%%\begin{eqnarray}
%%u(p,\lambda)_\pm & = & (E\pm\lambda|{\bf p}|)^{1/2}\chi_\lambda(p) , \\
%%v(p,\lambda)_\pm & = & \pm\lambda(E\mp\lambda|{\bf p}|)^{1/2}\chi
%%_{-\lambda}(p)
%%\end{eqnarray}
%%\end{mathletters}
%%
%%%% This section contains more display math examples, including unnumbered
%%%% equations (displaymath environment). The last paragraph includes some
%%%% examples of in-line math featuring a couple of the AASTeX symbol macros.
%%
%%\section{Floating material and so forth}
%%
%%%% The displaymath environment will produce the same sort of equation as
%%%% the equation environment, except that the equation will not be numbered
%%%% by LaTeX.
%%
%%Consider a task that computes profile parameters for a modified
%%Lorentzian of the form
%%\begin{equation}
%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
%%\end{equation}
%%where
%%\begin{displaymath}
%%d_{1} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{displaymath}
%%d_{2} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{displaymath}
%%x_{1} = (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta
%%\end{displaymath}
%%\begin{displaymath}
%%y_{1} = -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
%%\end{displaymath}
%%
%%In these expressions $x_{0}$,$y_{0}$ is the star center, and $\Theta$ is the
%%angle with the $x$ axis.  Results of this task are shown in table~\ref{tbl-1}.
%%It is not clear how these sorts of analyses may affect determination of
%% $M_{\sun}$, but the assumption is that the alternate results
%%should be less than 90\degr\ out of phase with previous values.
%%We have no observations of \ion{Ca}{2}.
%%Roughly \slantfrac{4}{5} of the electronically submitted abstracts
%%for AAS meetings are error-free.
%%
%%%% If you wish to include an acknowledgments section in your paper,
%%%% separate it off from the body of the text using the \acknowledgments
%%%% command.
%%
%%%% Included in this acknowledgments section are examples of the
%%%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
%%%% argument when you want to print the url directly in the text. Otherwise,
%%%% use either \url or \anchor, with the HREF as the first argument and the
%%%% text to be printed in the second.
%%
\acknowledgments
%chien peng, peter erwin
%%
%%We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
%%doing the math in section~\ref{bozomath}.
%%More information on the AASTeX macros package is available \\ at
%%\url{http://www.aas.org/publications/aastex}.
%%For technical support, please write to
%%\email{aastex-help@aas.org}.
%%
%%%% To help institutions obtain information on the effectiveness of their
%%%% telescopes, the AAS Journals has created a group of keywords for telescope
%%%% facilities. A common set of keywords will make these types of searches
%%%% significantly easier and more accurate. In addition, they will also be
%%%% useful in linking papers together which utilize the same telescopes
%%%% within the framework of the National Virtual Observatory.
%%%% See the AASTeX Web site at http://aastex.aas.org/
%%%% for information on obtaining the facility keywords.
%%
%%%% After the acknowledgments section, use the following syntax and the
%%%% \facility{} macro to list the keywords of facilities used in the research
%%%% for the paper.  Each keyword will be checked against the master list during
%%%% copy editing.  Individual instruments or configurations can be provided 
%%%% in parentheses, after the keyword, but they will not be verified.
%%
%%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
%%
%%%% Appendix material should be preceded with a single \appendix command.
%%%% There should be a \section command for each appendix. Mark appendix
%%%% subsections with the same markup you use in the main body of the paper.
%%
%%%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%%%% The equation counter will reset when it encounters the \appendix
%%%% command and will number appendix equations (A1), (A2), etc.
%%
%%\appendix
%%
%%\section{Appendix material}
%%
%%Consider once again a task that computes profile parameters for a modified
%%Lorentzian of the form
%%\begin{equation}
%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
%%\end{equation}
%%where
%%\begin{mathletters}
%%\begin{displaymath}
%%d_{1} = \frac{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{equation}
%%d_{2} = \case{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
%%\end{equation}
%%\begin{eqnarray}
%%x_{1} & = & (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta \\
%%y_{1} & = & -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
%%\end{eqnarray}
%%\end{mathletters}
%%
%%For completeness, here is one last equation.
%%\begin{equation}
%%e = mc^2
%%\end{equation}

@@

\bibliography{/Users/gsavorgnan/Dropbox/giulia_e_basta/Literature/SMBHbibliography}

%%\begin{thebibliography}{}
%%\bibitem[Auri\`ere(1982)]{aur82} Auri\`ere, M.  1982, \aap,
%%    109, 301
%%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
%%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
%%    McClintock, J. E.  1978, \apj, 224, 39
%%\bibitem[Djorgovski \& King(1984)]{djo84} Djorgovski, S.,
%%    \& King, I. R.  1984, \apjl, 277, L49
%%\bibitem[Hagiwara \& Zeppenfeld(1986)]{hag86} Hagiwara, K., \&
%%    Zeppenfeld, D.  1986, Nucl.Phys., 274, 1
%%\bibitem[Harris \& van den Bergh(1984)]{har84} Harris, W. E.,
%%    \& van den Bergh, S.  1984, \aj, 89, 1816
%%\bibitem[H\`enon(1961)]{hen61} H\'enon, M.  1961, Ann.d'Ap., 24, 369
%%\bibitem[Heiles \& Troland(2003)]{heiles03} Heiles, C. \& Troland, T. H., 2003, \apjs, preprint doi:10.1086/381753
%%\bibitem[Kim, Ostricker, \& Stone(2003)]{kim03} Kim, W.-T.,  Ostriker, E., \& Stone, J. M., 2003, \apj, 599, 1157
%%\bibitem[King(1966)]{kin66}  King, I. R.  1966, \aj, 71, 276
%%\bibitem[King(1975)]{kin75}  King, I. R.  1975, Dynamics of
%%    Stellar Systems, A. Hayli, Dordrecht: Reidel, 1975, 99
%%\bibitem[King et al.(1968)]{kin68}  King, I. R., Hedemann, E.,
%%    Hodge, S. M., \& White, R. E.  1968, \aj, 73, 456
%%\bibitem[Kron et al.(1984)]{kro84} Kron, G. E., Hewitt, A. V.,
%%    \& Wasserman, L. H.  1984, \pasp, 96, 198
%%\bibitem[Lynden-Bell \& Wood(1968)]{lyn68} Lynden-Bell, D.,
%%    \& Wood, R.  1968, \mnras, 138, 495
%%\bibitem[Newell \& O'Neil(1978)]{new78} Newell, E. B.,
%%    \& O'Neil, E. J.  1978, \apjs, 37, 27
%%\bibitem[Ortolani et al.(1985)]{ort85} Ortolani, S., Rosino, L.,
%%    \& Sandage, A.  1985, \aj, 90, 473
%%\bibitem[Peterson(1976)]{pet76} Peterson, C. J.  1976, \aj, 81, 617
%%\bibitem[Rudnick et al.(2003)]{rudnick03} Rudnick, G. et al., 2003, \apj, 599, 847
%%\bibitem[Spitzer(1985)]{spi85} Spitzer, L.  1985, Dynamics of
%%    Star Clusters, J. Goodman \& P. Hut, Dordrecht: Reidel, 109
%%\bibitem[Treu et al.(2003)]{treu03} Treu, T. et al., 2003, \apj, 591, 53
%%\end{thebibliography}

@@

%% Use the figure environment and \plotone or \plottwo to include
%% figures and captions in your electronic submission.
%% To embed the sample graphics in
%% the file, uncomment the \plotone, \plottwo, and
%% \includegraphics commands
%%
%% If you need a layout that cannot be achieved with \plotone or
%% \plottwo, you can invoke the graphicx package directly with the
%% \includegraphics command or use \plotfiddle. For more information,
%% please see the tutorial on "Using Electronic Art with AASTeX" in the
%% documentation section at the AASTeX Web site, http://aastex.aas.org/
%%
%% The examples below also include sample markup for submission of
%% supplemental electronic materials. As always, be sure to check
%% the instructions to authors for the journal you are submitting to
%% for specific submissions guidelines as they vary from
%% journal to journal.

%% This example uses \plotone to include an EPS file scaled to
%% 80% of its natural size with \epsscale. Its caption
%% has been written to indicate that additional figure parts will be
%% available in the electronic journal.

%%\begin{figure}
%%\epsscale{.80}
%%\plotone{f1.eps}
%%\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
%%in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
%%\end{figure}
%%
%%\clearpage
%%
%%%% Here we use \plottwo to present two versions of the same figure,
%%%% one in black and white for print the other in RGB color
%%%% for online presentation. Note that the caption indicates
%%%% that a color version of the figure will be available online.
%%%%
%%
%%\begin{figure}
%%\plottwo{f2.eps}{f2_color.eps}

>>>>

\documentclass[preprint2]{emulateapj}

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/papers/lentiptical/images/}}

@@

\shorttitle{Lentiptical galaxies}
\shortauthors{Savorgnan \& Graham}

@@

\title{Lentiptical galaxies and their ordinary black holes}

@@

\begin{abstract}
Lentiptical galaxies are an intermediate class of galaxies between elliptical  
and lenticular galaxies.
Lentipticals are early-type, bulge-dominated galaxies that feature a fast-rotating, 
intermediate-scale disk of stars embedded within a slow-rotating spheroid of stars.
Such spheroid dominates the light in the central region of the galaxy and also at large radii, 
unlike lenticular galaxies, whose bulge is encased within a (more extended) large-scale disk. 
Lentiptical galaxies have often been confused with lenticular galaxies and,
consequently, their bulge luminosities have been largely underestimated. 
This surprisingly common mistake has led to some wrong conclusions, 
such as the claim that a number of lentiptical galaxies are extreme outliers 
in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
i.e. these galaxies host a central black hole whose mass, $M_{\rm BH}$, is abnormally large 
compared to expectations from their (underestimated) bulge stellar mass, $M_{\rm *,sph}$.

\end{abstract}

@@

@@

There are currently two well-known types of stellar disks in galaxies. 
The first are the large-scale disks (with sizes of a few kpc)  
that dominate at large radii in spiral and lenticular galaxies; 
the second are the small (tens to a couple of hundred parsec) nuclear disks 
observed in both early- and late-type galaxies
(e.g. \citealt{scorzavandenbosch1998,rest2001,balcells2007,ledo2010}).
The origin of the nuclear disks has been speculated to arise 
from the infall of small satellite galaxies or gas clouds {\bf refs}.  
The origin, or at least the on-going feeding and growth, of the large-scale disks 
has been attributed to cold gas flows, gas rich mergers and halo accretion events 
(e.g. \citealt{khochfarsilk2006,dekel2009nat,dekel2009apj,ceverino2010,ceverino2012,conselice2012}).  
A thorough review can be found in Combes (arXiv:1309.1603 and 1405.6405). \\

A puzzling question, which has been unspoken for decades, 
is why are there not intermediate-sized disks; 
why are there not accretion events which create disks larger than the typical nuclear disks 
but which are not large enough to dominate at large radii? 
Here we report on the existence of these intermediate-sized stellar disks. \\

The existence of such disks is not only important for our understanding of disk growth in general, 
reducing or eliminating an old mystery, 
but accounting for such structure will impact on our galaxy scaling relations 
and surely see the reclassification of many ``disky'' elliptical galaxies 
and lenticular galaxies as \emph{lentiptical} 
galaxies with intermediate-sized stellar disks that do not dominate at large radii. \\

It is well known to the astronomers that identifying a face-on, featureless stellar disk 
in an early-type galaxy only by looking at the galaxy image 
is a very challenging if not even impossible task. 
Luckily, the majority of such disks are observed by us with some level of inclination, 
which makes them appear as flat, elliptical components, 
and helps us distinguishing them from the more spherical galaxy bulges. 
A more subtle and overlooked issue is the difficulty in identifying the extent of these disks 
with respect to their bulge.

Kinematic maps, obtained from IFU spectroscopy, constitute an extremely powerful instrument to this purpose. 
{\bf However, xxxSLUGGS have shown that the limited FOV of the atlas3d maps is not enough to get the full picture,
and more extended maps are needed to reveal which galaxies display a FR behaviour all the way out 
and which ones become SR at large radii.}
Unfortunately, kinematic maps are not yet available for a large sample of galaxies in the local Universe. 
Notwhithstanding, there is another powerful instrument that can help identify the extent of 
stellar disks in early-type galaxies, 
and that has the advantage of requiring only galaxy images (even photometrically uncalibrated), 
which are cheaper to acquire in terms of telescope time than IFU observations. 
This instrument is the ellipticity profile of a galaxy's isophotes, 
that can be easily obtained from a 1D isophotal analysis of the galaxy image, 
using for example the IRAF task {\tt ellipse}.

The toy model shown in Figure \ref{fig:ellp} illustrates the typical ellipticity profile 
for a large-scale disk that encases a bulge, as in lenticular (S0) galaxies, 
for an intermediate-scale disk embedded in a larger spheroid, that we name lentiptical (E/S0) galaxy, 
and for an elliptical (E) galaxy featuring a nuclear stellar disk. 
Note that, in the case of an intermediate-scale disk, 
the maximum of the ellipticity profile corresponds to the minimum difference between the 
light profile of the bulge and that of the disk (vertical dashed line in Figure \ref{fig:ellp}). 
Galaxy modellers that attempt to perform bulge/disk decomposition of lentiptical galaxies 
should always check that their model correctly reproduces this important signature.

The {\bf realization, coscienza, not-knowledge} that many ``elliptical'' galaxies 
actually contain embedded stellar disks 
dates back at least three decades 
\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995,
donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 
more recently, intermediate-scale disks were all but unfamiliar to \cite{krajnovic2013}. 
However, the class of lentiptical galaxies has been missed out by many galaxy modellers, 
who labelled as ``unphysical'' the idea that an intermediate-sized stellar disk 
can exist fully embedded in a larger spheroidal component. 
This unspoken bias has led them to reject any bulge/disk decomposition with an outcome 
similar to that illustrated in the middle panel of Figure \ref{fig:ellp}. 
Unsurprisingly, some studies have found that the b/t ratio of S0s is less than...

Examples of lentiptical galaxies are the galaxies MRK 1216, NGC 1271, NGC 1277, NGC 1332, NGC 3115, NGC 3377 
(see Figure \ref{fig:n3377ex}) and NGC 4621. 
All of these galaxies can be easily described and explained with a simple two-component model: 
an outer S\'ersic bulge plus an embedded, intemediate-sized exponential\footnote{Given 
its close-to-edge-on inclination,  
the stellar disk of NGC 1332 is better described by a S\'ersic profile with S\'ersic index $n<1$ 
\citep{pastrav2013a,pastrav2013b}.} disk. 
Models that ``forzatamente'' describe the galaxy with an inner S\'ersic bulge 
encased within a large-scale exponential disk can produce acceptable fits ???? statistically decent??
only in two cases:
either the data are shallow, thus they are not probing the re-rise of the bulge, 
or an outer Sersic halo is added to the model to account for the outer light (n3115 and n3377 lasker).....

show vel map? + ell profile, explain shape

our models are physically motivated and produce bulge luminosities which make these galaxies no longer outliers
btw they are not outliers on the M-Mgal relation, which suggests poor bulge/disk decomposition

people that do only 2d decompositions, should still perform a 1d isophotal analysis to check extent of disk

\begin{figure}
\includegraphics[width=\columnwidth]{diskextent.eps}
\caption{Illustration of the typical light profile (top plots) and ellipticity profile (bottom plots) of a galaxy 
featuring a stellar disk with varying size. 
For simplicity, we show separately the light profile of the bulge (or spheroid) in red 
and that of the disk in blue. 
The sum of these two contributions gives the galaxy's light profile (not represented here).
The left panel shows the case of a large-scale disk, {\bf prototipico} of a barless lenticular galaxy. 
The right panel displays the case of an elliptical galaxy with a nuclear stellar disk. 
The middle panel presents the case of a lentiptical galaxy with an inermediate-sized disk. 
Stellar disks typically have fixed ellipticity, dictated by their inclination to our line of sight.
Bulges, instead, can have their ellipticities varying with radius,
but they are usually rounder than inclined disks, 
thus their average ellipticity is lower than that of an inclined disk.
If the ellipticity profile of a galaxy increases with radius, 
this can be ascribed to an inclined disk that becomes progressively more important over the bulge,
whereas a radial decrease of ellipticity signifies the opposite case. 
Therefore the ``shape'' of the ellipticity profile can be decisive to distiguish between 
large- and intermediate-scale disks. 
}
\label{fig:ellp}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{n3377ex.eps}
\caption{
}
\label{fig:n3377ex}
\end{figure}

The existence of intermediate-scale stellar discs suggests that a continuum of disc sizes may exist, rather than a dichotomy of nuclear vs. large-scale discs.  
In a somewhat similar vein, it was previously thought that bulges came in just one of two flavours: 
classical bulges with n=4 light profiles and pseudobulges with n=1 light profiles (e.g. Carollo et al. 1998-2002?).  
Although many works still advocate this bulge dichotomy based on their light profiles, Graham \& Worley (2008) have revealed no 
evidence for a bimodality in the distribution of their Sersic indices from a sample of 400 disc 
galaxies\footnote{The co-existence of classical and pseudo bulges in the same galaxy (e.g. Erwin et al. 2003, ApJ, 597, 929) 
further blurs claims for galaxies having either a classical bulge or a pseudobulge.}.   
The presence of intermediate-scale discs blurs the distinction between elliptical and lenticular galaxies and it may be that our E vs S0 
classification for galaxies without spiral arms could be better represented by a range of bulge-to-disc (luminosity and size) ratios.

@@

\acknowledgments
luca cortese, peppo gavazzi, matteo fossati
%%
%%We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
%%doing the math in section~\ref{bozomath}.
%%More information on the AASTeX macros package is available \\ at
%%\url{http://www.aas.org/publications/aastex}.
%%For technical support, please write to
%%\email{aastex-help@aas.org}.
%%
%%%% To help institutions obtain information on the effectiveness of their
%%%% telescopes, the AAS Journals has created a group of keywords for telescope
%%%% facilities. A common set of keywords will make these types of searches
%%%% significantly easier and more accurate. In addition, they will also be
%%%% useful in linking papers together which utilize the same telescopes
%%%% within the framework of the National Virtual Observatory.
%%%% See the AASTeX Web site at http://aastex.aas.org/
%%%% for information on obtaining the facility keywords.
%%
%%%% After the acknowledgments section, use the following syntax and the
%%%% \facility{} macro to list the keywords of facilities used in the research
%%%% for the paper.  Each keyword will be checked against the master list during
%%%% copy editing.  Individual instruments or configurations can be provided 
%%%% in parentheses, after the keyword, but they will not be verified.
%%
%%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
%%
%%%% Appendix material should be preceded with a single \appendix command.
%%%% There should be a \section command for each appendix. Mark appendix
%%%% subsections with the same markup you use in the main body of the paper.
%%
%%%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%%%% The equation counter will reset when it encounters the \appendix
%%%% command and will number appendix equations (A1), (A2), etc.
%%
%%\appendix
%%
%%\section{Appendix material}
%%
%%Consider once again a task that computes profile parameters for a modified
%%Lorentzian of the form
%%\begin{equation}
%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
%%\end{equation}
%%where
%%\begin{mathletters}
%%\begin{displaymath}
%%d_{1} = \frac{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{equation}
%%d_{2} = \case{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
%%\end{equation}
%%\begin{eqnarray}
%%x_{1} & = & (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta \\
%%y_{1} & = & -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
%%\end{eqnarray}
%%\end{mathletters}
%%
%%For completeness, here is one last equation.
%%\begin{equation}
%%e = mc^2
%%\end{equation}

@@

\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}

@@
